\pkg{MRP-Kit} A `grammar' of multilevel regression with post-stratification and implementation in \proglang{R}

### 2021-03-03 paper/paper_joss/paper_joss.Rmd
Start updating paper.

---
documentclass: jss
author:
  - name: Lauren Kennedy
    affiliation: Monash University
    email: \email{name@company.com}
    url: http://rstudio.com
  - name: Mitzi Morris
    affiliation: Columbia University
  - name: Jonah Gabry
    affiliation: Columbia University
  - name: Rohan Alexander
    affiliation: University of Toronto
title:
  formatted: "\\pkg{MRP-Kit} A 'grammar' of multilevel regression with post-stratification and implementation in \\proglang{R}"
  # If you use tex in the formatted title, also supply version without
  plain:     "A 'grammar' of multilevel regression with post-stratification and implementation in R"
  # For running headers, if needed
  short:     "\\pkg{foo}: A grammar of MRP"
abstract: >
  In this paper we define a grammar for multilevel regression with post-stratification (MRP) and implement this grammar in the R Package \pkg{MRPKit}. Our grammar is centered around the following verbs: add, remove, delete, and replace. These act on survey objects. Our grammar, and its implementation, provides a detailed workflow when conducting MRP that will be useful for researchers and in teaching.
keywords:
  # at least one keyword must be supplied
  formatted: [multilevel regression with post-stratification, "\\proglang{R}", reproducibility, statistics, political science]
  plain:     [multilevel regression with post-stratification, R, reproducibility, statistics, political science]
preamble: >
  \usepackage{amsmath}
output: rticles::jss_article
---

@@

Our grammar and package complements existing packages such as \proglang{survey} (ADD CITATION), X and Y. These packages... Instead, ours is focused on what is needed for MRP.

@@

The most common alternative at the moment to this package is for users to do all aspects themselves. While there is nothing conceptually difficult about MRP, the implementation can be difficult. In particular, preparing and matching different levels between surveys can be time consuming and potentially introduce errors.

HERE

Survey package

Declare design

DIY

MRP package - https://github.com/gelman/mrp

And how we're different

@@

@@

% sampl <- surveyStr$new(...)
% pop <- surveyStr$new(...)
% map <- surveyMap$new(sampl, pop, ...)
% mrp1 <- MRP$new(sampl, pop, map)

% option 1
% mod1 <- mrp1$fit(y ~ x + (1|group))
% mod1 <- mrp1$fit(y ~ x + (1|group) + (1|group2))

% mod1$poststratify()
% mod2$poststratify("model1")

% or

% option 2
% mrp1$fit(y ~ x + (1|group), name = "model1")
% mrp1$fit(y ~ x + (1|group) + (1|group2), name = "model2")

% mrp1$poststartify("model1")
% mrp1$poststartify("model2")

What is the difference between add and new? What is replace doing? URGH, I just need to look at the repo.

@@

>>>>

---
documentclass: jss
author:
  - name: Lauren Kennedy
    affiliation: Monash University
    email: \email{lauren.kennedy729@gmail.com}
    url: https://jazzystats.com
  - name: Mitzi Morris
    affiliation: Columbia University
  - name: Jonah Gabry
    affiliation: Columbia University
  - name: Rohan Alexander
    affiliation: University of Toronto
title:
  formatted: "\\pkg{MRP-Kit} A 'grammar' of multilevel regression with post-stratification and implementation in \\proglang{R}"
  # If you use tex in the formatted title, also supply version without
  plain:     "A 'grammar' of multilevel regression with post-stratification and implementation in R"
  # For running headers, if needed
  short:     "\\pkg{MRP-Kit}: A grammar of MRP"
abstract: >
  In this paper we define a 'grammar' for multilevel regression with post-stratification (MRP) and implement this grammar in the R Package \pkg{MRPKit}. Our grammar is centered around the following verbs: add, remove, delete, and replace. These act on survey objects. Our grammar, and its implementation, provides a detailed workflow when conducting MRP that will be useful for researchers and in teaching.
keywords:
  # at least one keyword must be supplied
  formatted: [multilevel regression with post-stratification, "\\proglang{R}", reproducibility, statistics, political science]
  plain:     [multilevel regression with post-stratification, R, reproducibility, statistics, political science]
preamble: >
  \usepackage{amsmath}
output: rticles::jss_article
bibliography: references.bib
---

@@

Our grammar and package complements existing packages such as \proglang{survey} [@lumleyone, @lumleytwo, @lumleythree], and \proglang{DeclareDesign} [@citeDeclareDesign]. These packages are focused on the designing, implementing, and simulating from, surveys. Instead, ours is focused on what is needed for MRP.

@@

The most common alternative at the moment to this package is for users to do all aspects themselves. While there is nothing inherently difficult about MRP, the implementation can be difficult. In particular, preparing and matching different levels between surveys can be time consuming and potentially introduce undocumented errors.

The \proglang{survey} package [@lumleyone, @lumleytwo, @lumleythree] ...

The \proglang{DeclareDesign} package [@citeDeclareDesign]...

There is also an existing package called \proglang{MRP} available here: https://github.com/gelman/mrp. However it does not appear to have been updated in some time.

The main alternative approach is for MRP to be conducted on a case-specific basis. That is a researcher interested in MRP estimates, writes the code needed to obtain, clean, prepare, analyze and ultimately interpret the estimates. Again, while there is nothing inherently wrong with this approach, successfully conducting MRP requires dealing with a large number of small issues. Each of these is small in their own right, but getting them wrong can have large effects that are potentially unnoticed on the estimates.

@@

new()
validate() 
add() 
delete() 
replace()
validate()
mapping()
tabulate()
fit() 
predictify() 
collapsify() 
visify()

@@

<!-- #' feline_prefs = SurveyObj$new( -->
<!-- #'   feline_survey[,c("age1","gender","pet_own","y")], -->
<!-- #'   questions = c("Please identify your age group","Please select your gender","Which pet do you own?", "Response"), -->
<!-- #'   responses = list(levels(feline_survey$age1),levels(feline_survey$gender),levels(feline_survey$pet_own),c("no","yes")), -->
<!-- #'   weights = feline_survey$wt, -->
<!-- #'   design = formula("~.") -->
<!-- #' ) -->
<!-- #' popn_obj = SurveyObj$new( -->
<!-- #'   approx_popn[,c("age2","gender","pet_pref")], -->
<!-- #'   questions = c("Which age group are you?","Gender?","Which pet would you like to own?"), -->
<!-- #'   responses = list(levels(approx_popn$age2),levels(approx_popn$gender),levels(approx_popn$pet_pref)), -->
<!-- #'   weights = approx_popn$wt, -->
<!-- #'   design = formula("~.") -->
<!-- #' ) -->
<!-- #' q1 <- question$new( -->
<!-- #'   name = "age", -->
<!-- #'   col_names = c("age1","age2"), -->
<!-- #'   values_map = list( -->
<!-- #'     "18-25" = "18-35", "26-35" = "18-35","36-45" = "36-55", -->
<!-- #'     "46-55" = "36-55", "56-65" = "56-65", "66-75" = "66+", "76-90" = "66+" -->
<!-- #'   ) -->
<!-- #' ) -->
<!-- #' q2 <- question$new( -->
<!-- #'   name = "pet", -->
<!-- #'   col_names = c("pet_own","pet_pref"), -->
<!-- #'   values_map = list("cat" = "cat", "kitten" = "cat","dog" = "dog","puppy" = "dog") -->
<!-- #' ) -->
<!-- #' q3 <- question$new( -->
<!-- #'   name = "gender", -->
<!-- #'   col_names = c("gender","gender"), -->
<!-- #'   values_map = data.frame("male" = "m","female" = "f", "nonbinary" = "nb") -->
<!-- #' ) -->
<!-- #' -->
<!-- #' tmp_map <- SurveyMap$new(samp_obj = feline_prefs, popn_obj = popn_obj, q1) -->
<!-- #' print(tmp_map) -->
<!-- #' tmp_map$validate() -->
<!-- #' tmp_map$add(q3) -->
<!-- #' print(tmp_map) -->
<!-- #' tmp_map$delete(q3) -->
<!-- #' print(tmp_map) -->
<!-- #' tmp_map$add(q3) -->
<!-- #' tmp_map$delete("gender") -->
<!-- #' print(tmp_map) -->
<!-- #' tmp_map$add(q2) -->
<!-- #' print(tmp_map) -->
<!-- #' tmp_map$replace(q1,q3) -->
<!-- #' print(tmp_map) -->
<!-- #' tmp_map$add(q1) -->
<!-- #' print(tmp_map) -->
<!-- #' tmp_map$validate() # TODO: figure out why this errors -->
<!-- #' tmp_map$mapping() -->
<!-- #' tmp_map$tabulate("age") #Just use age in the poststrat matrix -->
<!-- #' tmp_map$tabulate() #Use all variables in the map -->
<!-- #' -->
<!-- #' -->
<!-- #' mod_fit_1 <- tmp_map$fit( -->
<!-- #'   fun = rstanarm::stan_glmer, -->
<!-- #'   formula = y ~ (1|age) + (1|gender), -->
<!-- #'   family = "binomial", -->
<!-- #'   refresh = 100, -->
<!-- #'   cores = 2 -->
<!-- #' ) -->
<!-- #' -->
<!-- #' mod_fit_2 <- tmp_map$fit( -->
<!-- #'   fun = brms::brm, -->
<!-- #'   formula = y ~ (1|age) + (1|gender), -->
<!-- #'   family = "bernoulli", -->
<!-- #'   refresh = 100, -->
<!-- #'   cores = 2 -->
<!-- #' ) -->
<!-- #' -->
<!-- #' class(mod_fit_1) -->
<!-- #' -->
<!-- #' # predict in postrat matrix - returns a matrix -->
<!-- #' # with rows as poststrat rows, cols as posterior samples. -->
<!-- #' poststrat_fit <- tmp_map$predictify(mod_fit_2) -->
<!-- #' -->
<!-- #' # get an estimate for a particular variable level or population -->
<!-- #' # arguments: -->
<!-- #' # - output of "predictify" -->
<!-- #' # - (optional) variable name -->
<!-- #' # body: -->
<!-- #' # - if no variable name then compute population estimate -->
<!-- #' # - if variable name specified compute weighted mean (N_j * theta)/sum(N_j) -->
<!-- #' # return type: -->
<!-- #' # - data.frame -->
<!-- #' #   - one column if popn estimate, otherwise one column per level of variable -->
<!-- #' #   - one row per posterior sample -->
<!-- #' sae_preds <- tmp_map$collapsify(poststrat_fit, variable_aggr = "age") -->
<!-- #' popn_preds <- tmp_map$collapsify(poststrat_fit) -->
<!-- #' plot1 <- tmp_map$visify(sae_preds) -->
<!-- #' plot1 -->
<!-- #' plot2 <- tmp_map$visify(popn_preds) -->
<!-- #' plot2 -->

@@

\subsection*{Simulated data}

### 2021-03-03 paper/paper_joss/paper_joss.tex
Start updating paper.

\Plainauthor{Lauren Kennedy, Mitzi Morris, Jonah Gabry, Rohan Alexander}
\Plaintitle{A `grammar' of multilevel regression with post-stratification and
implementation in R}
\Shorttitle{\pkg{foo}: A grammar of MRP}

\Abstract{
In this paper we define a grammar for multilevel regression with
post-stratification (MRP) and implement this grammar in the R Package
\pkg{MRPKit}. Our grammar is centered around the following verbs: add,
remove, delete, and replace. These act on survey objects. Our grammar,
and its implementation, provides a detailed workflow when conducting MRP
that will be useful for researchers and in teaching.
}

@@

@@

Our grammar and package complements existing packages such as
\proglang{survey} (ADD CITATION), X and Y. These packages\ldots{}
Instead, ours is focused on what is needed for MRP.

@@

The most common alternative at the moment to this package is for users
to do all aspects themselves. While there is nothing conceptually
difficult about MRP, the implementation can be difficult. In particular,
preparing and matching different levels between surveys can be time
consuming and potentially introduce errors.

HERE

Survey package

Declare design

DIY

MRP package - \url{https://github.com/gelman/mrp}

And how we're different

@@

\% sampl \textless- surveyStr\(new(...) % pop <- surveyStr
\)new(\ldots) \% map \textless-
surveyMap\(new(sampl, pop, ...) % mrp1 <- MRP
\)new(sampl, pop, map)

\% option 1 \% mod1 \textless-
mrp1\(fit(y ~ x + (1|group)) % mod1 <- mrp1
\)fit(y \textasciitilde{} x + (1\textbar group) + (1\textbar group2))

\% mod1\(poststratify() % mod2
\)poststratify(``model1'')

\% or

\% option 2 \% mrp1\(fit(y ~ x + (1|group), name = "model1") % mrp1
\)fit(y \textasciitilde{} x + (1\textbar group) + (1\textbar group2),
name = ``model2'')

\% mrp1\(poststartify("model1") % mrp1
\)poststartify(``model2'')

@@

>>>>

\Plainauthor{Lauren Kennedy, Mitzi Morris, Jonah Gabry, Rohan Alexander}
\Plaintitle{A `grammar' of multilevel regression with
post-stratification and implementation in R}
\Shorttitle{\pkg{MRP-Kit}: A grammar of MRP}

\Abstract{
In this paper we define a `grammar' for multilevel regression with
post-stratification (MRP) and implement this grammar in the R Package
\pkg{MRPKit}. Our grammar is centered around the following verbs: add,
remove, delete, and replace. These act on survey objects. Our grammar,
and its implementation, provides a detailed workflow when conducting MRP
that will be useful for researchers and in teaching.
}

@@

% Pandoc citation processing

@@

Our grammar and package complements existing packages such as
\proglang{survey} \citep[\citet{lumleytwo},
\citet{lumleythree}]{lumleyone}, and \proglang{DeclareDesign}
\citep{citeDeclareDesign}. These packages are focused on the designing,
implementing, and simulating from, surveys. Instead, ours is focused on
what is needed for MRP.

@@

The most common alternative at the moment to this package is for users
to do all aspects themselves. While there is nothing inherently
difficult about MRP, the implementation can be difficult. In particular,
preparing and matching different levels between surveys can be time
consuming and potentially introduce undocumented errors.

The \proglang{survey} package \citep[\citet{lumleytwo},
\citet{lumleythree}]{lumleyone} \ldots{}

The \proglang{DeclareDesign} package \citep{citeDeclareDesign}\ldots{}

There is also an existing package called \proglang{MRP} available here:
\url{https://github.com/gelman/mrp}. However it does not appear to have
been updated in some time.

The main alternative approach is for MRP to be conducted on a
case-specific basis. That is a researcher interested in MRP estimates,
writes the code needed to obtain, clean, prepare, analyze and ultimately
interpret the estimates. Again, while there is nothing inherently wrong
with this approach, successfully conducting MRP requires dealing with a
large number of small issues. Each of these is small in their own right,
but getting them wrong can have large effects that are potentially
unnoticed on the estimates.

@@

@@

\bibliography{references.bib}
